Short Paper

### 2022-01-24 AppHumanGHY.Rmd
CHanges

journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: aag.csl
output: rticles::elsevier_article
---

>>>>

journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
#linenumbers: true
#numbersections: true
csl: csl/aag.csl
output: rticles::elsevier_article
---

### 2022-01-24 AppHumanGHY.tex
CHanges

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% Pandoc header

\begin{document}
\begin{frontmatter}

@@

Here are two sample references: (Dirac 1953; Feynman and Vernon Jr.;
1963).

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Dirac1953888}{}}%
Dirac, P. A. M. 1953.
\href{https://doi.org/10.1016/S0031-8914(53)80099-6}{The lorentz
transformation and absolute time}. \emph{Physica} 19
(1-\/--12):888--896.

\leavevmode\vadjust pre{\hypertarget{ref-Feynman1963118}{}}%
Feynman, R. P., and F. L. Vernon Jr. 1963.
\href{https://doi.org/10.1016/0003-4916(63)90068-X}{The theory of a
general quantum system interacting with a linear dissipative system}.
\emph{Annals of Physics} 24:118--173.

\end{CSLReferences}

>>>>

\usepackage{lineno} % add

@@

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\begin{frontmatter}

@@

Here are two sample references: (\textbf{Feynman1963118?};
\textbf{Dirac1953888?}).

@@
